How do psychology journals handle post-publication critique? A cross-sectional study of policy and practice.

### 2024-11-12 manuscript/manuscript_NHB.Rmd
Added via the Open Science Framework

---
title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication
  Critiques"
author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault,
  R. T., & Hardwicke, T. E.
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  word_document: default
abstract: "Fostering critical discussion is essential to upholding the ethos of science
  as an unbiased, collaborative, and self-correcting endeavor. Journals can support
  this by offering options for post-publication critique, such as commentaries or
  letters, allowing peers to voice substantiated concerns of empirical articles. We
  provide a descriptive, cross-sectional analysis of post-publication critique policies
  and prevalence across samples of a) 100 prominent and b) 100 randomly-selected and psychology journals.
  We found that 38% of prominent and 23% of randomly-selected psychology journals
  offered explicit critique options. Length and time-to-submit
  limits were often not stated. Critique prevalence was rare with only a single event
  identified among two samples of 101 articles. Given the widespread recognition of
  the replication crisis in psychology, allowing avenues for criticisms to be voiced
  may help increase credibility within the field. To support transparency and
  self-correction, psychology journals should offer clearly stated post-publication
  critique options and encourage their use.\n"
keywords: "post-publication critique, peer review, psychology, meta-research, journal
  policy, self-correction, scientific criticism"
bibliography: references.bib
link-citations: true
csl: nature.csl
floatsintext: false
figurelist: false
tablelist: false
footnotelist: false
linenumbers: true
mask: true
draft: true
always_allow_html: true
urlcolor: blue
---

```{r setup, include = FALSE}
library(papaja) # article template
library(tidyverse)
library(ggplot2) # figure creation
library(ggrepel) # for ggplot text labels
library(patchwork) # for multipanel plot layouts
library(RColorBrewer) # data visualisation
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(binom) # for calculating CIs
library(citation) # for organizing citations
library(tinytex)
library(english) # for displaying code generated numbers as written 
```

```{r echo=FALSE, message=FALSE}
# Load processed data files
#'ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique',
d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data

@@

```{r echo=FALSE, message=FALSE}
# Create separate tibbles for Prominent and Randomly-selected journal samples

@@

# Main
*Add 'Introduction' section*

# Results

## Part 1: Post-Publication Critique Policies

For descriptive statistics on journal subdisciplines, post-publication critique acceptance, and COPE membership for both prominent and randomly-selected samples, see Supplementary Information ##. A full list of the journals included in this study, along with their post-publication critique options and restrictions, is provided in Supplementary Information ##.

## Prominent Psychology Journals

```{r prominent journal-characteristics, echo=FALSE, message=FALSE}

# Ascertain prominent journal JIF characteristics

promJournalCharacteristics <- dj_prominent %>% 
  filter(ppc_type == "A") %>%       # Keep only single entry for each journal
  summarise(promMedian_jif = round(median(jif),2), 
            promMin_jif = round(min(jif),2),
            promMax_jif = round(max(jif),2),
            promIQR_jif = round(IQR(jif),2)
  )

>>>>

---
title: "How do psychology journals handle post-publication critique? A cross-sectional study of policy and practice."
author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault, R. T., & Hardwicke, T. E.
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  word_document: default
abstract: "Post-publication critique, such as letters-to-the-editor, can contribute
  to the validity and trustworthiness of scientific research. We conducted a cross-sectional
  and (b) prominent psychology journals. In 2023, an explicit submission option for
  post-publication critique was available at 23% (95% CI [16% to 32%]) of randomly
  sampled psychology journals (N = 100) and 38% of the most prominent psychology journals
  (N = 100). Journals sometimes imposed limits on the length and time allowed to submit
  critiques. We manually inspected two random samples of empirical articles published
  in 2020 (N = 101 articles per sample), estimating the prevalence of post-publication
  critique to be 0% (95% CI [0% to 3.7%]) in psychology journals generally and 1%
  (95% CI [0.2% to 5.4%]) in the most prominent psychology journals. The policy and
  practice of post-publication critique is seriously neglected in psychology journals.\n"
keywords: "post-publication critique, meta-research, journal policy, self-correction,
  peer review"
bibliography: references.bib
link-citations: true
csl: "CSL-apa.csl"
always_allow_html: true
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
#library(papaja) # article template
library(tidyverse)
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(tidylog) # for inline code feedback
library(here) # for finding files
library(binom) # for calculating CIs
library(citation) # for organizing citations
library(tinytex)
library(english) # for displaying code generated numbers as written 
```

```{r}
# Load processed data files
#'ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique',
d_articles <- read_csv(here('data', 'processed', 'd_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data', 'processed', 'd_journals.csv'), show_col_types = F) # journal data

@@

```{r}
# Custom function to convert text to sentence case
sentence_case <- function(x) {
  s <- tolower(x)
  substr(s, 1, 1) <- toupper(substr(s, 1, 1))
  s
}
```

```{r}
# Create separate tibbles for Prominent and Randomly-selected journal samples

@@

\newpage

# Research transparency statement

**Conflicts of interest:** All authors declare no conflicts of interest. **Funding:** This research was supported by Australian Research Council grant FT210100652. **Artificial intelligence:** No artificial intelligence assisted technologies were used in this research or the creation of this article. **Ethics:** Not applicable. **Preregistration:** The study protocol (aims, methods, and analyses) was preregistered [(https://osf.io/d6xf2)](https://osf.io/d6xf2) on April 19th 2023, prior to data collection which began on May 10th 2023. There were no major deviations from the preregistered protocol; minor deviations are reported in Supplementary Table A1. **Materials:** All study materials are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/). **Data:** All primary data are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/). **Analysis scripts:** All analysis scripts are publicly available [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/). **Computational reproducibility:** The analysis code is available in a Code Ocean container [(https://codeocean.com/capsule/4794801/tree)](https://codeocean.com/capsule/4794801/tree) which re-creates the software environment in which the original analyses were performed.

# Introduction

Critical discourse can contribute to the validity and trustworthiness of scientific research [@robertk.merton1973; @vazire2022]. Criticism can highlight errors, limitations, and alternative interpretations, helping research consumers to calibrate their beliefs in scientific claims. However, the proliferation of poor-quality research in psychology (and other fields) indicates that the dominant mode of critical discourse, conventional peer review, is not sufficient to maintain high standards in the scientific literature [@hardwicke2020; @nosek2022].

Scientific journals can support the ongoing critical scrutiny of research by offering avenues for post-publication critique, such as letters to the editor [@altman2002]. Journals’ obligation to facilitate post-publication critique is explicitly codified in the principles of the Committee on Publication Ethics (COPE), an organisation that most prominent journals are members of [@committeeonpublicationethics2021; @hardwicke2022]. However, prior research indicates that many (37%) of the most prominent academic journals across a broad range of scientific disciplines do not explicitly allow submissions of post-publication critique [@hardwicke2022]. Moreover, journals that do allow post-publication critiques in principle rarely publish them in practice, and often impose restrictive limits on length and time-to-submit. The present research closely follows the methods used in @hardwicke2022 but extends this prior work by providing a focused evaluation of how psychology journals in particular handle post-publication critique (Hardwicke et al. examined 15 journals in a combined psychiatry and psychology category, along with 315 journals from other disciplines).

For the purposes of the present study, we operationally defined post-publication critique as any journal-based avenue for sharing peer-initiated critical discourse related to specific research articles previously published in the same journal (see Supplementary Information B for a complete operational definition). A prototypical example of post-publication critique is a letter to the editor, though there are other variations, such as commentary articles and website comments.

Our study was conducted in two parts. The first part aimed to describe policies related to post-publication critique at: (a) all psychology journals publishing empirical research (via a random sample of 100 journals), and (b) the 100 most prominent^[There is no agreed upon or objective measure of journal prominence. To avoid an entirely subjective and arbitrary definition, we used Journal Impact Factor as a proxy for journal prominence. Journal Impact Factor, like all journal metrics, has limitations (especially when used as a proxy for quality, which is not what we are doing here), but using this method yields a collection of journals that we believe has good face validity in terms of prominence.] psychology journals publishing empirical research. Specifically, we identified whether options for submitting critiques (e.g., letters to the editor) are available, and whether limits are imposed in terms of length, time-to-submit since publication of the target article, number of references, and whether critiques were sent for independent peer review. The second part of our study aimed to estimate the prevalence of post-publication critiques published in: (a) all psychology journals (via a random sample of 100 empirical psychology articles), and (b) the 100 most prominent psychology journals (via a random sample of 100 empirical articles published in these journals).

# Part One: Post-Publication Critique Policies

## Method

The methods and analysis plan were preregistered [(https://osf.io/d6xf2)](https://osf.io/d6xf2). All deviations from the preregistered protocol were considered minor and are detailed in Supplementary Information A and, where relevant, mentioned below.

### Design

This investigation had a cross-sectional design. All measured variables are described in detail in Supplementary Table C1. In brief, we extracted and described journal policies related to post-publication critique (according to our operational definition, Supplementary Information B) provided on journal websites in 2023. We recorded the name and description of any options for post-publication critique offered by each journal (e.g., article types such as ‘letters’ or ‘commentaries’, or web comments) or any explicit statement that the journal does not accept post-publication critique; limits imposed on post-publication critique in terms of length (e.g., number of words), time-to-submit (e.g., weeks since publication of the target article) and/ or number of references; and whether it was stated that post-publication critiques would be sent for independent external peer review (i.e., reviews solicited from individuals who were not members of the editorial team or authors of the target article). We recorded qualitative as well as quantitative limits; for example, a length limit might be stated as “500 words” or “short”. We also identified whether journals were members of COPE, an organisation which outlines several core publishing practices, including the importance of facilitating post-publication critique [@committeeonpublicationethics2021].

### Sample

*Target populations*

The target populations of the two samples of journals were: (a) all psychology journals publishing empirical research in 2023; and (b) prominent journals in psychology publishing empirical research in 2023. We were only interested in legitimate (non-predatory), peer-reviewed journals.

*Sample sizes*

The sample consisted of 100 randomly selected journals and 100 prominent journals. Justification for these sample sizes was based on a precision analysis (details provided in Supplementary Information E). Eleven journals appeared in both samples and were not replaced in order to maintain the random sampling scheme.

*Preparing samples (inclusion/exclusion criteria)*

We only included journals that were in the Web of Science Core Collection, meaning they met 24 basic quality criteria, such as having a peer-review policy and publishing scholarly content (for details see https://perma.cc/C5J3-V7C4). As of 15th March 2023, there were 867 unique journals included in this database that were classified as belonging to a subject category related to ‘psychology’. Of these 867 journals, 115 were classified by Web of Science as non-English language and excluded, leaving 752 journals remaining. 
For the random sample of psychology journals, a list of all included 752 psychology journals was randomly shuffled using the R function ‘sample’ and we selected the first 600 on the shuffled list (to allow for exclusions). For the prominent journals sample, we sorted journals in order of their 2021 Clarivate Journal Impact Factors (https://jcr.clarivate.com/) and selected the first 600 journals (to allow for exclusions). The list of these journals is available at https://osf.io/k6yx5. For both samples, journals were then evaluated sequentially from the top of their respective list until the target of 100 eligible journals in each sample was reached. If a journal needed to be excluded after manual inspection, it was replaced with the next available journal in its list, thus maintaining the respective sampling schemes.
We excluded an additional 6 journals from the randomly-selected journal list and 15 from the prominent list because they did not publish empirical research. This determination involved some degree of subjective judgement and was primarily based on each journal’s scope as defined on its website. If the journal’s description of its scope was ambiguous, we searched the journal's archive for examples of empirical articles to inform our determination. This represented a slight deviation from the preregistered protocol (for details see Supplementary Information A).

### Procedure

*Piloting and training*

The data extraction procedures were piloted with 10  journals that were not included in the sample. All investigators were trained and familiarised with the data extraction process and practised with positive and negative training examples.

*Collating journal policy information*

One investigator (AW or NM) identified, downloaded, and archived the ‘scope’ and ‘article types’ sections (or equivalent) provided on each journal’s website [(https://osf.io/8k7m4/)](https://osf.io/8k7m4/). This information was used to determine whether the journal published empirical articles and, if so, whether post-publication critique article types were accepted by the journal. If these sections could not be found, a second investigator (TEH) double-checked.

*Data extraction*

The policy information (outlined in Supplementary Information C using a Goole Form [(https://osf.io/d6uzj)](https://osf.io/d6uzj) was extracted and classified for each journal by two investigators. Primary coding was conducted by AW (n = 183) and NM (n = 37). Secondary coding was conducted by RTT (n = 82), SV (n = 80), and TEH (n = 41).  Disagreements between primary and secondary coders, usually arising due to unclear descriptions of article types, were resolved by TEH. This was necessary for 40 journals (for details see Supplementary Information H).
For coding whether journals provided an option for post-publication critique, we first examined the journal website’s description of the journal’s article types (typically found in journals’ submission guidelines or instructions to authors). If a journal’s description of its article types was not provided or unclear, we searched the journal's archive to see if any examples of articles meeting our operational definition of post-publication critique (Supplementary Information B) had been published within the last five years (i.e., since the beginning of 2019). Note that if a journal had an article type that sounded like it might be used for post-publication critique (e.g., "Commentary"), that was not sufficient for a positive classification; the description of the article type, or examples of that article type, also had to meet our operational definition of post-publication critique (see Supplementary Information B).

*Data harmonization*

Journals used various naming conventions for similar types of post-publication critique and various units (e.g., characters, words or pages for length limits) to specify limits. To address this, we harmonised the various names used for critique formats to four types (letters [to the editor], commentaries, web comments, and other) and transformed length limit units to words and time-to-submit limit units to weeks (for details see Supplementary Information G).

## Results

### Journal characteristics

```{r}
# Calculate JIF median and IQR for random journals
randomJIF <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  summarise(Median = round(median(jif),2),
            Q1 = round(quantile(jif, .25),2),
            Q3 = round(quantile(jif, .75),2),
            IQR = round(IQR(jif),2)
  )
```

```{r}
# Calculate JIF median and IQR for prominent journals
prominentJIF <- dj_prominent %>% 
  filter(ppc_type == "A") %>%      # Keep only single entry for each journal
  summarise(Median = round(median(jif),2), 
            Q1 = round(quantile(jif, .25),2),
            Q3 = round(quantile(jif, .75),2),
            IQR = round(IQR(jif),2)
  )
```

```{r}
# Count randomly selected journals listed as COPE members
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())
```

```{r}
# Count prominent journals listed as COPE members 
prominentCOPE <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())
```

The median 2021 Journal Impact Factor was `r randomJIF$randMedian_jif` (interquartile range = `r randomJIF$Q1` - `r randomJIF$Q3`) for the randomly sampled journals (NB. 25 of the randomly selected journals did not have Journal Impact Factors) and `r prominentJIF$Median` (interquartile range = `r prominentJIF$Q1` - `r prominentJIF$Q3`) for the prominent journals. `r randomCOPE` of the `r dj_random %>% filter(ppc_type == 'A') %>% nrow()` randomly sampled journals, and `r prominentCOPE` of the `r dj_prominent %>% filter(ppc_type == 'A') %>% nrow()` prominent journals, were members of COPE. Journal characteristics stratified by psychology sub-field are available in Supplementary Information I.

### How many journals offer post-publication critique?

```{r}
# Inspect how frequently PPC policies were stated for randomly selected journals 
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()
```

```{r}
# Calculate confidence interval for explicitly stated PPC policies among randomly selected journals
randomPPCyes <- dj_random %>%
  filter(ppc_type == 'A', !is.na(ppc_name)) %>%
  summarise(count = n())

randomPPCno <- dj_random %>%
  filter(ppc_type == 'A', is.na(ppc_name)) %>%
  summarise(count = n())

# Sepcify sample size and confidence interval of 95%
sample_size <- 100
confidence_level <- 0.95

# CIs for 'Yes Explicit'
randomPPC_CI <- binom.confint(randomPPCyes, sample_size, method = "wilson", conf.level = confidence_level)

# CIs for 'No' (both explicit and Implicit)
randomPPC_CI_neg <- binom.confint(randomPPCno, sample_size, method = "wilson", conf.level = confidence_level)
```

```{r}
# Return all rows with ppc_name values for ppc_type B and C indicating > 1 PPC type
random_multiPPC <- dj_random %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) 
```

```{r}
# Inspect the COPE status of randomly selected journals with and without PPC policies
randomCOPE <- dj_random %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercent = round((COPE_count / total_count) * 100)) %>%
 ungroup()
```

A full list of journals and their post-publication critique options and limits is provided in Supplementary Information J (raw data available at [https://osf.io/8k7m4/](https://osf.io/8k7m4/)). Among the 100 randomly-selected journals, `r randomPPC$count[randomPPC$has_ppc == "YES"]` (`r randomPPC$count[randomPPC$has_ppc == "YES"]`%, 95% CI [`r round(randomPPC_CI[1,5]*100)`%, `r round(randomPPC_CI[1,6]*100)`%]) explicitly stated that they allowed submissions of post-publication critique. Of these `r randomPPC$count[randomPPC$has_ppc == "YES"]` journals, `r print(as.character(english(nrow(random_multiPPC))))` had two types of critique formats and the other `r (randomPPC$count[randomPPC$has_ppc == "YES"] - nrow(random_multiPPC))` each had one critique format. `r print(as.character(english(randomPPC$count[randomPPC$has_ppc == "NO EXPLICIT"])))` journal (*Clinical Psychology: Science and Practice*, also included in the prominent journals sample) stated explicitly that they did not accept post-publication critique. `r dj_random %>% filter(ppc_name == "Commentary") %>% nrow()` journals offered commentaries, `r dj_random %>% filter(ppc_name == "Letters") %>% nrow()` journals offered letters, `r dj_random %>% filter(ppc_name == "Web comments") %>% nrow()` journals offered web comments, and `r print(as.character(english(nrow(dj_random %>% filter(ppc_name == "Other")))))` journal (*Cortex*) offered a format called 'verification reports' which we classified as ‘other’. Of the `r randomPPC$count[randomPPC$has_ppc == "YES"]` journals that explicitly accepted post-publication critique, `r randomCOPE$COPE_count[randomCOPE$has_ppc == "YES"]` (`r randomCOPE$COPEpercent[randomCOPE$has_ppc == "YES"]`%) were COPE members. Of the `r randomCOPE$COPE_count[randomCOPE$has_ppc == "NO"]` journals that did not have a policy related to post-publication critique, `r randomCOPE$COPE_count[randomCOPE$has_ppc == "NO"]` (`r randomCOPE$COPEpercent[randomCOPE$has_ppc == "NO"]`%) were COPE members.

```{r}
# Inspect how frequently PPC policies were stated for prominent journals 
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()
```

```{r}
# Get names for prominent journals that offered more than one type of PPC
prom_multiPPC <- dj_prominent %>%
  filter((ppc_type == "B" | ppc_type == "C") & (!is.na(ppc_name))) 
```

```{r}
# Inspect the COPE status of prominent journals with and without PPC policies
promCOPE <- dj_prominent %>%
 filter(ppc_type == "A") %>%
 mutate(has_ppc = case_when(
    has_ppc == "NO EXPLICIT" ~ "NO",
    has_ppc == "NO IMPLICIT" ~ "NO",
    TRUE ~ has_ppc
 )) %>%
 group_by(has_ppc) %>%
 summarise(
    total_count = n(),
    COPE_count = sum(cope == TRUE)
 ) %>%
 mutate(COPEpercent = round((COPE_count / total_count) * 100)) %>%
 ungroup()
```

Among the 100 prominent journals, `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` (`r prominentPPC$count[prominentPPC$has_ppc == "YES"]`%) explicitly stated that they allowed submissions of post-publication critique^[Confidence intervals are not included for the prominent psychology journals as this sample represents our entire population of interest, negating the need for inferential statistical calculations.]. Of these `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` journals, `r print(as.character(english(nrow(prom_multiPPC))))` had two types of critique format and the other `r (prominentPPC$count[prominentPPC$has_ppc == "YES"] - nrow(prom_multiPPC))` journals had one critique format. `r print(as.character(english(prominentPPC$count[prominentPPC$has_ppc == "NO EXPLICIT"])))` journals (*Clinical Psychology: Science and Practice* and *Psychological Bulletin*) stated explicitly that they did not accept post-publication critiques. No reason was provided. `r dj_prominent %>% filter(ppc_name == "Commentary") %>% nrow()` journals offered commentaries, `r dj_prominent %>% filter(ppc_name == "Letters") %>% nrow()` journals offered letters, and `r dj_prominent %>% filter(ppc_name == "Web comments") %>% nrow()` journals offered web comments. Of the `r prominentPPC$count[prominentPPC$has_ppc == "YES"]` journals that explicitly accepted post-publication critique, `r promCOPE$COPE_count[promCOPE$has_ppc == "YES"]` (`r promCOPE$COPEpercent[promCOPE$has_ppc == "YES"]`%) were COPE members. Of the `r promCOPE$COPE_count[promCOPE$has_ppc == "NO"]` journals that did not have a policy related to post-publication critique, `r promCOPE$COPE_count[promCOPE$has_ppc == "NO"]` (`r promCOPE$COPEpercent[promCOPE$has_ppc == "NO"]`%) were COPE members.

### What limits did journals place on post-publication critique?

```{r}
# Find the most restrictive length limit of any journal
minLength <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_name),
         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
 mutate(quantLength = as.numeric(ppc_length)) %>%
 slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
 ungroup()

# Find the most restrictive time limit of any journal
minTime <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_name),
         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
 mutate(quantTime = as.numeric(ppc_time)) %>%
 slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
 ungroup()
```

Table 1 (randomly selected journals) and Table 2 (prominent journals) show the limits journals imposed on post-publication critique in terms of length, time-to-submit, and number of references. The tables also show whether a peer review policy for critiques was stated. Length limits were stated for most critique formats, especially those in prominent journals. Length limits were usually stated quantitatively (e.g., “1,000 words”). A few formats had qualitative limits (e.g., “brief”). Letters had tighter length limits than commentaries on average. The most restrictive length limit was `r minLength$quantLength` words at the *Journal of Adolescent Health*. Time-to-submit limits were not stated for most critique formats; they were somewhat more common in prominent journals. Time-to-submit limits, when present, were often stated qualitatively (e.g., “brief”) and sometimes quantitatively (e.g., “3 months”). The most restrictive time-to-submit limit was `r minTime$quantTime` weeks at the *Journal of Applied Psychology*. For most critique formats, journals did not state whether they would be sent for independent peer review or not. For a full list of stated limits at each journal, see Supplementary Information J.

\newpage
\begin{landscape}

\textbf{Table 1.} Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits. 
```{r}
# Check length limits placed on PPC options in randomly selected journals

# Summarise length statistics for All Types
randomLengthAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomLengthAll_1 <- randomLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
randomLengthType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = round(median(quantLength, na.rm = TRUE)),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1) 
 ) %>%
  ungroup()

# Put results into desired table format
randomLengthType_1 <- randomLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomLength_combo <- bind_rows(
  randomLengthType_1,
  randomLengthAll_1
)
```

```{r}
# Check time-to-submit limits placed on PPC options in prominent journals

# Summarise time-to-submit statistics for All Types
randomTimeAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1) 
 )

# Put results into desired table format
randomTimeAll_1 <- randomTimeAll %>% 
  mutate('Post-publication critique type' = "All Types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
randomTimeType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomTimeType_1 <- randomTimeType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomTime_combo <- bind_rows(
  randomTimeType_1,
  randomTimeAll_1
)
```

```{r}
# Check reference limits placed on PPC options in prominent journals

# Summarise reference statistics for All Types
randomRefAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomRefAll_1 <- randomRefAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
randomRefType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomRefType_1 <- randomRefType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
randomRef_combo <- bind_rows(
  randomRefType_1,
  randomRefAll_1
)
```

```{r}
# Check how many PPC options are sent for external peer review in prominent journals
